
\pdfpagewidth 8.5in
\pdfpageheight 11in
\pdfhorigin 1in
\pdfvorigin 1in

\nopagenumbers
\parindent=0pt

\font\rm=ptmr at 10pt
\font\bf=ptmb at 10pt
\font\it=ptmri at 10pt
\font\sl=ptmbo at 10pt
\font\tt=pcrr at 10pt
\font\tb=pcrb at 10pt
\font\zdb=pzdr at 10pt
\font\lgrm=ptmr at 24pt
\font\smrm=ptmr at 9pt
\font\superrm=ptmr at 8pt

\def\super#1{\lower -.5ex \hbox{\superrm #1}}
\def\xmrk{{\zdb 4}}

\rm

{\lgrm Christopher L.~Rorvick\hfill\vbox{\smrm
\hbox to 3in {\hfil
1321 Kimball Court\quad $\bullet$\quad Naperville, IL~~60540}
\hbox to 3in {\hfil
(630) 416-0382\quad $\bullet$\quad chris@rorvick.com}
}}

\vskip 5pt \hrule \vskip 10pt

\long\def\section#1#2{\leftskip 1in \noindent\llap{\hbox to 1in {\bf #1\hss}}{#2}\vskip 10pt}
\long\def\lastsection#1#2{\leftskip 1in \noindent\llap{\hbox to 1in {\bf #1\hss}}{#2}}
\long\def\subsection#1#2{{\sl #1}\hfill{\bf #2}}
\def\bulleted#1#2{\setbox0=\hbox{#1\ }\hangindent=\wd0#1 #2}


\section{PROFILE}{%
Software designer with fourteen years experience producing high quality
solutions across multiple industries using many technologies.
Eight years in the financial industry focusing on low-latency systems
and infrastructure supporting automated trading.
}

\section{EDUCATION}{%
{\bf University of Illinois}\quad Urbana--Champaign\par
\subsection{B.S.~in Computer Science}
    {May 2000}
}

\section{EXPERIENCE}{%
\parskip=5pt
{\bf KCG Holdings, Inc.}\quad Chicago, IL

One of the world's largest independent market makers, combining
advanced technology with exceptional client service to deliver
liquidity, lower transaction costs, and improve pricing.

\vskip 5pt
\subsection{Software Developer, Messaging}
    {November 2015 -- Present}

Member of a small team responsible for the firm's proprietary IPC stack.

\bulleted{$\bullet$}{%
Solicited input from traders to understand operational difficulties with
extensible data-interchange technology.  Implemented scheme to robustly
detect incompatibles between publishers and subscribers and refactored
code to remove significant redundancy.
}

\bulleted{$\bullet$}{%
Fixed a number of long-standing bugs through experimentation in lab and
studying packet captures.  This included resolving problems with
sequencing and malformed message headers.
}

\vskip 5pt
\subsection{Software Developer, Tick to Trade}
    {November 2014 -- October 2015}

Worked on core trading platform focusing on technologies for trade
simulation and replay.

\bulleted{$\bullet$}{%
Added replay capabilities to Python-embedded signal-processing
framework.
}

\bulleted{$\bullet$}{%
Participated in working group to determine simulation priorities.
Worked with another developer on a Python API for running replays in the
cluster environment.
}

\bulleted{$\bullet$}{%
Identified opportunities to improve automation and robustness in our
processes.  Championed solutions using technologies including Git and
Docker including a general framework for running builds and regression
tests on local workstations with minimal requirements from the host
environment.
}

\vskip 10pt

{\bf Cognitive Capital, LLC}\quad Chicago, IL

Liquidity provider to capital markets using proprietary automated trading
technology.

\vskip 5pt
\subsection{Software Engineer}
    {April 2012 -- May 2014}

Member of core development team responsible for company's distributed
trading platform consisting of a hierarchy of multi-threaded C++
services.

\bulleted{$\bullet$}{%
Designed and implemented major overhaul of execution subsystem with
focus on improving signal attribution and coordination of various
execution components.  Design considerations included reducing thread
contention and improving cache efficiency.
}

\bulleted{$\bullet$}{%
Implemented new real-time signals as C++ services using specifications
from financial engineering.  Worked with portfolio managers on rollout
including facilitating rotational studies, data analysis, and
implementing reporting of nightly parameterization.
}

\bulleted{$\bullet$}{%
Planned and implemented migration of CVS repositories to Git.  Retooled
substantial legacy automation and designed integration process for
nightly build.  Prepared training material and led instructional
sessions
}

\vskip 10pt

{\bf TradeLink, LLC}\quad Chicago, IL

Trading firm participating in a range of asset classes including
securities, futures, and options.

\vskip 5pt
\subsection{Software Designer, Algorithmic Trading \& Execution}
    {September 2010 -- February 2012}

Responsible for maintaining and deploying software for firm's two
algorithmic trading platforms and implementing and maintaining trading
strategies within these platforms.

\bulleted{$\bullet$}{%
Optimized trading of a \$40 million portfolio by migrating execution
logic from legacy Python platform to C++ smart order router.
Reduced latency by roughly four milliseconds per transaction.
}

\bulleted{$\bullet$}{%
Analyzed execution for a high frequency FX basis trade.
Automated reporting of time-series data pulled from disparate sources
into consolidated plots.
Recommended and implemented several optimizations included refactoring
the top-level execution logic, bug fixes to the feed handler, and
tuning the network stack.
}

\bulleted{$\bullet$}{%
Implemented FIX trading interface within firm's C++ trading platform
providing trading strategies with direct connectivity to exchanges.
}

\subsection{Software Designer / Technical Lead, Application Development}
    {January 2007 -- August 2010}

Developed and maintained many applications and infrastructure
components critical to the firm.
Managed development efforts including providing design and technical
direction to other developers.

\bulleted{$\bullet$}{%
Designed and implemented distribution framework for market data
via shared memory with C++ API.
Significantly reduced load on network infrastructure and trader
workstations allowing groups to participate and profit on high-volume
events that were previously not tradeable at the firm.
}

\bulleted{$\bullet$}{%
Managed a project to allow execution desk traders to monitor hundreds of
positions across the portfolios of its managed funds.  Included C++
libraries, server, and client application.
}

\bulleted{$\bullet$}{%
Maintained C++ screen trading application displaying a ``price ladder''
including aggregate book and trade volumes.  Supported click trading and
auto-spreads.
}

\bulleted{$\bullet$}{%
Implemented multi-threaded C++ feed handler for Eurex's
{\it New Socket Datafeed} providing non-netted, low-latency price data
to fixed income group operating in London office.
}

\vskip 5pt
\subsection{Software Developer, Application Development}
    {June 2005 -- June 2006}

Maintained a number of trading applications and back office software
critical to the day-to-day operations of the firm.

\bulleted{$\bullet$}{%
Enhanced and maintained a suite of C++ options trading applications
including two auto-traders and a program for monitoring implied
volatilities in real-time.
}

\bulleted{$\bullet$}{%
Responsible for maintaining firm's legacy Java platform including
post-trade and back-office applications.  
Automated build process and refactored code base into versioned
reusable modules.
}

\bulleted{$\bullet$}{%
One of two developers maintaining and providing 24x7 production support
for clearing system.
Implemented Python modules for processing semi-standard and
firm-specific data formats.
}

\vskip 10pt

{\bf Impact Forensics, LLC}\quad Chicago, IL
    \hfill{July 2006 -- December 2006}

\vskip 10pt

{\bf U.S.~Cellular Corp.}\quad Bensenville, IL
    \hfill{February 2003 -- May 2005}

\vskip 10pt

{\bf Universal Access, Inc.}\quad Chicago, IL
    \hfill{April 2001 -- April 2002}

\vskip 10pt

{\bf Second Millennium Consulting, Inc.}\quad Chicago, IL
    \hfill{January 2000 -- March 2001}
}
\vfil\eject

\section{PUBLIC}{%
\parskip=3pt
\subsection{Linux kernel}    {\tb https://github.com/torvalds/linux.git}

\bulleted{$\bullet$}{%
Worked with ALSA subsystem maintainer to move Line 6 sound driver out of
staging and into the mainline tree.  Refactored code, fixed bugs, and
reviewed and tested other changes.
}

\bulleted{$\bullet$}{%
Refactored USB EHCI debug port definitions into their own header.  This
allows drivers for the quirky FOTG210 and FUSBH200 USB host controllers
to pull these definitions in rather than redefining the interface
themselves, removing about 100 lines of redundant code.
}

\vskip 8pt

\subsection{Git}                    {\tb https://github.com/git/git.git}

\bulleted{$\bullet$}{%
Added support for per author time zones to {\tt cvsimport(1)} command.
Allows commit log timestamps to be associated with appropriate UTC
offsets.
}

\bulleted{$\bullet$}{%
References are generally allowed to update when pushing to a remote
repository if the new commit is a descendent of the old.  Added logic to
reject ``fast-forwarding'' a tag unless it is forced (e.g., with the
{\tt -{-}force} option.)
}

\bulleted{$\bullet$}{%
Various additions and updates to documentation.
}

\vskip 8pt

\subsection{CVSps}       {\tb https://git.gitorious.org/cvsps/cvsps.git}

Eric S.\ Raymond took over CVSps in late 2012 and added an option to
dump a CVS repository to a Git {\tt fast-import(1)} stream.  Tested
development tree for these changes and contributed numerous patches.

\vskip 8pt

\subsection{Hobson Village directory}
                      {\tb https://github.com/crorvick/hv-directory.git}

Automated generation of neighborhood directory saving many hours of
volunteer time annually.  Wrote a Perl script to convert CSV input data
into \TeX\ which is then used to generate PDF output ready for printing.
}

\section{SKILLS}{%
{\bf Programming:} C, C++, Perl, Python, Java

{\bf Scripting:} Bourne/Bash, Sed, AWK, Tcl, Autotools, Make, SQL

{\bf Version control:} Git, CVS, Subversion, SCCS

{\bf Databases:} PostgreSQL, Sybase, MySQL, Oracle

{\bf Data analysis:} R, gnuplot, Octave

{\bf Operating systems:} Gentoo and Redhat/Fedora Linux, Solaris, HP-UX

{\bf Libraries:} Boost, Intel TBB, pthreads, Armadillo, ACE, GTK+

{\bf Miscellaneous:} Docker, TCP/IP networking, GNU software, \TeX
}

\section{TRAINING}{%
\xmrk\quad LinuxCon 2014 and 2015

\xmrk\quad Astoria Seminar: Extraordinary C++
% http://herbsutter.com/2007/08/31/plug-for-the-astoria-seminar/

\xmrk\quad Sun Certified Programmer for the Java 2 Platform

\xmrk\quad Application Development for WebSphere MQ 5.3

\xmrk\quad Application Development for Tuxedo 6.5

\xmrk\quad HP-UX Administration for Experienced UNIX Administrators

}

% Need to be smarter about how \section is defined so that the \vskip
% at the end doesn't cause an empty page.
\lastsection{OTHER}{%
Den Leader -- Cub Scout Pack 503\hfill
2015 -- present\par

Uber badge winner -- DEF CON Hacking Conference\hfill
2015\par

Treasurer -- Hobson Village Community Association\hfill
2008 -- 2012\par

Board member -- Hobson Village Community Association\hfill
2006 -- 2008\par

Officer -- Triangle Fraternity, Alpha Chapter\hfill
1997 -- 1998

Eagle Scout -- Boy Scouts of America\hfill
1994%
}
\end
